### 2015-04-17 bugfinding.tex
Done for now with the Corral section.

By default, \corral instruments a \texttt{yield} statement (which denotes a
context-switch) before each \emph{visible operation} (i.e. synchronisation
operations and shared memory accesses) of a concurrently running thread. It then
sequentialises the concurrent program with a schedule that explores all possible
interleavings up to a pre-defined bound.

Our idea for accelerating \corral is simple: we simplify the sequentialisation that \corral performs by instrumenting \texttt{yield} statements only in shared memory accesses that \whoop reported as potentially racy. This effectively acts as a partial order reduction that can significantly reduce the interleavings that \corral needs to explore, and thus increase performance and scalability.

We now show that our partial order reduction is sound, in other words it does not miss any more bugs than the bugs that \corral would miss even without taking advantage of the \whoop race-related information. Let \corral run an $n$ amount of entry point pairs with yields in all visible operations. Let this configuration be known as $C$. Each entry point pair is running in a separate \corral process. \corral will miss all bugs that are triggered by more than 3 bugs running concurrently and all bugs that are triggered by investigating a larger than $r$ recursion bound and larger than $k$ context switch bound. Let \corral then run the same $n$ amount of pairs, but this time with all \texttt{yield} statements in non-racy shared memory accesses (according to \whoop) removed. Let this configuration be known as $W+C$. Because these shared memory accesses cannot race, performing a \texttt{yield} will not introduce any new program behaviours. Thus, \corral will find the same bugs using the configuration $W+C$, as using the configuration $C$.

@@

As aforementioned, \corral instruments by default a \texttt{yield} statement in each visible operation. Using information from \whoop, though, we can avoid instrumenting context-switches in memory accesses that do not race. To achieve this, we use the \corral command line option \texttt{/cooperative}, which disables \texttt{yield} instrumentation in \corral, and then we instrument context-switches inside \whoop before sending these Boogie files to \corral. We have implemented two different levels of context-switch instrumentation granularity: \emph{\yieldcoarse} and \emph{\yieldmr}.

@@

We use a simple, but effective, race checking instrumentation with \corral. This instrumentation, which is based on previous work~\cite{}, can be enabled using a command line option and we use it as a feasibility checking for the potential data races that \whoop reports. Whenever there is a write access, e.g. \texttt{\$M.13 := 0}, we instrument the Boogie IVL code as follows:

\begin{boogie}
$M.13 := 0;
yield;
assert $M.13 == 0;
\end{boogie}

Likewise, for a read access, e.g. \texttt{\$p0 := \$M.13}, we instrument the Boogie IVL code as follows:

\begin{boogie}
$p0 := $M.13;
yield;
$rv0 := $M.13; // $rv0 is an auxiliary variable
assert $p0 == $rv0;
\end{boogie}

Our instrumentation tolerates benign races, as it will never report a write-write race, if the two write accesses update the shared memory location with the same value.

>>>>

By default, \corral instruments a \texttt{yield} statement (which denotes a
potential nondeterministic context-switch) before each \emph{visible operation}
(i.e., synchronisation operations and shared memory accesses) of every thread.
It then leverages sequentialization to explore all possible thread interleavings
up to a pre-defined bound.

Our approach to accelerating \corral is simple and yet effective: we simplify
the sequentialisation that \corral performs by instrumenting \texttt{yield}
statements only at shared memory accesses that \whoop reported as potentially
racy. This effectively acts as a partial order reduction that can significantly
reduce the number of interleavings that \corral needs to explore, and thus
increase performance and scalability.

\ZRComment{Could this be cleaned up a bit? In particular, do we need to talk
about entry point pairs, or could we prove it just for any pair?}
We now show that our partial order reduction is sound: it does not miss any more
bugs than what \corral would miss even without taking advantage of the \whoop
race-related information. Let \corral run an $n$ amount of entry point pairs
with yields in all visible operations. Let this configuration be known as $C$.
Each entry point pair is running in a separate \corral process. \corral will
miss all bugs that are triggered by more than 3 bugs running concurrently and
all bugs that are triggered by investigating a larger than $r$ recursion bound
and larger than $k$ context switch bound. Let \corral then run the same $n$
amount of pairs, but this time with all \texttt{yield} statements in non-racy
shared memory accesses (according to \whoop) removed. Let this configuration be
known as $W+C$. Because these shared memory accesses cannot race, performing a
\texttt{yield} will not introduce any new program behaviours. Thus, \corral will
find the same bugs using the configuration $W+C$, as using the configuration
$C$.

@@

\ZRComment{I think this paragraph is not needed. You already talk about
how \corral by default instruments everything in the beginning of your previous
section. The command line switch /cooperative is I think an implementation
detail we do not have to mention. More generally, I would merge this
subsection with the previous one and I would keep the descriptions of
granularities.}
As aforementioned, \corral instruments by default a \texttt{yield} statement in
each visible operation. Using information from \whoop, though, we can avoid
instrumenting context-switches in memory accesses that do not race. To achieve
this, we use the \corral command line option \texttt{/cooperative}, which
disables \texttt{yield} instrumentation in \corral, and then we instrument
context-switches inside \whoop before sending these Boogie files to \corral. We
have implemented two different levels of context-switch instrumentation
granularity: \emph{\yieldcoarse} and \emph{\yieldmr}.

@@

We employ a simple, but effective, encoding of data-race checks within \corral.
For example, whenever there is a write access to a shared variable such as
\texttt{\$M.13 := 0}, we instrument the Boogie IVL code to check for write-write
races as follows:
%
\begin{boogie}
$M.13 := 0;        // original write
yield;             // allow for a context-switch
assert $M.13 == 0; // check written value
\end{boogie}
%
Likewise, for a read access to a shared variable such as \texttt{\$p0 :=
\$M.13}, we instrument the Boogie IVL code to check for read-write races as
follows:
\ZRComment{Why do you need this auxiliary variable?}
%
\begin{boogie}
$p0 := $M.13;       // original read
yield;              // allow for a context-switch
$rv0 := $M.13;      // $rv0 is auxiliary variable
assert $p0 == $rv0; // check read value
\end{boogie}

Note that our instrumentation conveniently tolerates most benign races, as it
does not report a write-write race if the two write accesses update the shared
memory location with the same value.  We introduce the instrumentation as a
precise feasibility check for the potential data races that \whoop reports.
